% Curriculum Vitae template from https://github.com/gboeing/cv

\RequirePackage[l2tabu,orthodox]{nag} % warn if using any obsolete commands
\documentclass[11pt,letterpaper]{report} % document style

% load encoding and font packages for pdflatex, in order
\usepackage[T1]{fontenc}    % output 8-bit encoded fonts
\usepackage[utf8]{inputenc} % allow input of utf-8 encoded characters
\usepackage{ebgaramond}     % document's serif font
\usepackage{tgheros}        % document's sans serif font

% load babel, csquotes, and microtype in order
\usepackage[USenglish]{babel} % auto-regionalize hyphens, quote marks, etc
\usepackage[strict,autostyle]{csquotes} % smart and nestable quote marks
\usepackage[babel=true]{microtype} % enable micro-typographic adjustments

% load everything else
\usepackage{datetime} % enable formatting of date output
\usepackage{enumitem} % enumerate with [resume] option
\usepackage{geometry} % manually set page margins
\usepackage{setspace} % custom line spacing
\usepackage{tabto}    % make nice tabbing
\usepackage{titlesec} % allow custom section fonts

% load hyperref last for compatibility
\usepackage{hyperref} % enable hyperlinks and pdf metadata

% what is your name?
\newcommand{\myname}{Alyssa Lu Lee}

% how far to tab for list items with left-aligned date: different fonts need different widths
\newcommand{\listtabwidth}{1.7cm}

% define font to use as document's title
\newcommand{\namefont}[1]{{\normalfont\bfseries\Huge{#1}}}

% set section heading fonts and before/after spacing
\SetTracking{encoding=*, family=\sfdefault}{30} % increase heading font tracking
\titleformat{\section}{\lsstyle\sffamily\small\bfseries\uppercase}{}{}{}{}
\titlespacing{\section}{0pt}{30pt plus 4pt minus 4pt}{8pt plus 2pt minus 2pt}

% set subsection heading fonts and before/after spacing
\titleformat{\subsection}{\lsstyle\sffamily\footnotesize\bfseries}{}{}{}{}
\titlespacing{\subsection}{0pt}{16pt plus 4pt minus 4pt}{4pt plus 2pt minus 2pt}

% set page margins (assumes letter paper)
\geometry{body={6.5in, 9.0in},
    left=1.0in,
    top=1.0in}

% prevent paragraph indentation
\setlength\parindent{0em}

% set line spacing
\setstretch{0.9}

% define space between list items
\newcommand{\listitemspace}{0.25em}

% make unordered lists without bullets and use compact spacing
\renewenvironment{itemize}
{\begin{list}{}{\setlength{\leftmargin}{0em}
                \setlength{\parskip}{0em}
                \setlength{\itemsep}{\listitemspace}
                \setlength{\parsep}{\listitemspace}}}
{\end{list}}

% make tabbed lists so content is left-aligned next to years
\TabPositions{\listtabwidth}
\newlist{tablist}{description}{3}
\setlist[tablist]{leftmargin=\listtabwidth,
    labelindent=0em,
    topsep=0em,
    partopsep=0em,
    itemsep=\listitemspace,
    parsep=\listitemspace,
    font=\normalfont}

% print only the month and year when using \today
\newdateformat{monthyeardate}{\monthname[\THEMONTH] \THEYEAR}

% define hyperlink appearance and metadata for pdf properties
\hypersetup{
    colorlinks  = true,
    urlcolor    = black,
    citecolor   = black,
    linkcolor   = black,
    pdfauthor   = {\myname},
    pdfkeywords = {},
    pdftitle    = {\myname: Curriculum Vitae},
    pdfsubject  = {Curriculum Vitae},
    pdfpagemode = UseNone
}

\begin{document}
    \raggedright{}

    % display your name as the document title
    \namefont{\myname}

    % affiliation and contact info blocks
    \vspace{1em}
    \begin{minipage}[t]{0.700\textwidth}
        % current primary affiliation, left-aligned
        PhD Student \\
        Institute for Quantitative Biomedicine \\
        Rutgers University -- New Brunswick
    \end{minipage}
    \begin{minipage}[t]{0.295\textwidth}
        % contact info details, right-aligned
        \raggedleft{}
        \href{mailto:alyssa.lee@rutgers.edu}{alyssa.lee@rutgers.edu}
    \end{minipage}


    \section*{Education}

    \begin{tablist}

        \item[PhD] \tab{}\textbf{Quantitative Biomedicine}, Rutgers University, 2025--
        \tab{}Advised by Dr. Rohan Maddamsetti and Dr. Sagar Khare \\
        \item[BS]  \tab{}\textbf{Computational Biology}, Carnegie Mellon University, 2020--2024

    \end{tablist}



    \section*{Experience}

    \begin{tablist}

        \item[2026--present]   \tab{}\textbf{Research Fellow} \\
        \tab{}Institute for Quantitative Biomedicine\\
        \tab{}Rutgers University -- New Brunswick

        \item[2024--2025]   \tab{}\textbf{Bioinformatics Analyst} \\
        \tab{}Bioinformatics Core, Department of Pediatrics, School of Medicine\\
        \tab{}University of Pittsburgh

        \item[2023] \tab{}\tab{}\textbf{Nonclinical Research and Development Intern} \\
        \tab{}Bristol Myers Squibb

        \item[2022--2023] \tab{}\textbf{Undergraduate Research Assistant} \\
        \tab{}Machine Learning Department\\
        \tab{}Carnegie Mellon University

        \item[2022] \tab{}\tab{}\textbf{Software Engineer Intern} \\
        \tab{}CNH Industrial

    \end{tablist}



    \section*{Research Areas}

    \begin{itemize}

        \item AI methods for protein design
        \item Phage-host binding

    \end{itemize}



    \section*{Publications}

    \subsection*{Preprints and Submitted Manuscripts}

    \begin{tablist}

        
        \item[2026] \textbf{Lee, A. L.}, Sharma, A., \& Maddamsetti, R. (2026). \textit{Zero-shot ecological annotation of microbial genomes with myLLannotator accelerates scientific discovery} (p. 2026.01.18.700140) [preprint]. \textit{bioRxiv}. https://doi.org/10.64898/2026.01.18.700140
        \item[2026] Zaky, S. H., Rajasundaram, D., \textbf{Lee, A. L.}, Summersgill, K., Levine, S., Boulos, O., Intini, G., Sfeir, C., \& Silva, R. M. (2026). \textit{Using Spatial Transcriptomics to Identify a Diagnostic Molecular Signature Associated with Reversible Dental Pulpitis} [preprint]. Research Square. https://doi.org/10.21203/rs.3.rs-7955718/v1
        
        \item[2026] Jacoby, M. L., Sun, C., Farren, J. L., Marti, M. M., \textbf{Lee, A. L.}, Donovan, T., Klein, R., Rajasundaram, D., \& Klimstra, W. B. (2026). \textit{Biphasic lymphoid tissue activation drives systemic innate immune responses to alphavirus infection} [Manuscript submitted for publication].

    \end{tablist}

    \subsection*{Journal Articles}

    \begin{tablist}
        \item[2026] Kargl, C. K., Nindl, B. C., Goulart, J. B., Feigel, E. D., Sahu, A., Fazeli, P. K., \textbf{Lee, A. L.}, Rajasundaram, D., Ambrosio, F., Hubal, M. J., Lovalekar, M. T., Martin, B. J., Sterczala, A. J., \& Koltun, K. J. (2026). Varying Influence of Menstrual Cycle Phase and Hormonal Contraceptive Use on Resistance Exercise-Induced Circulating Extracellular Vesicle and Metabolite Signalling. \textit{Journal of Extracellular Vesicles}, 15(3), e70244. https://doi.org/10.1002/jev2.70244
        
    \end{tablist}




    \section*{Presentations}

    \begin{tablist}
        \item[2026] \tab{}\textbf{Lee, A. L.}, Sharma, A., \& Maddamsetti, R. (2026, March 12). \textit{myLLannotator: Using large language models for metadata annotation} [conference talk]. Rutgers Conference for Rising Stars in Graduate Research 2026, Rutgers University, New Brunswick, NJ.
        \item[2026] \tab{}\textbf{Lee, A. L.}, Seamann, A. L., Chung, G., Zhao, C., Khare, S.D. (2026, April 7). \textit{HaloMPNN: AI Redesign of Proteins for Salt Tolerance} [poster]. Sargassum Biorefinery Annual Meeting, Rutgers University, New Brunswick, NJ.

    \end{tablist}


    % display today's date as Month Year after a vertical space below the end of the text
    \begin{center}
        \vfill
        Updated \monthyeardate\today
    \end{center}

\end{document}
